Splints of root systems for special Lie subalgebras

### 2014-12-17 AffineLieAlgebras/Splints/special-paper.tex
Multiplicity-free modules, bibliography, general structure

@@

\begin{abstract}
  Splint of root system for simple Lie algebra appears naturally in studies of (regular) embeddings
  of reductive subalgebras. Splint can be used to construct branching rules. We consider special
  embedding of Lie subalgebra to Lie algebra. We classify projections of algebra root systems using
  extended Dynkin diagrams and single out the conditions of splint appearance and coincidence of
  branching coefficients with weight multiplicities.
\end{abstract}

@@

The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
is the decomposition of root system into disjoint union of images of two or more root systems.

Splint is defined as a decomposition of root system into disjoint union of images of two embeddings
of some other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$
is a bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with
vector composition law in $\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

@@

In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
coincidence of branching coefficients with weight multiplicities under certain conditions. 
\begin{Prop}
\begin{equation}
\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
\label{singular main-4}
\end{equation}
Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
\[
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
\]
\end{Prop}
%% Rewrite this property informally

In the present paper we consider special embeddings of Lie subalgebras into Lie algebra. In this
case root system of the subalgebra is not contained in the root system of the algebra. So the
original motivation for splints is not applicable. But we can consider the projection of root system
of algebra on the root space of the subalgebra. Such a projection is not a root system anymore, but
it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is possible to classify most
projections using Dynkin diagrams augmented with multiplicities. We then define splint for such
'weak' root systems and state the conditions of its appearance and implications for the calculation
of branching coefficients (Section \ref{sec:splints-spec-embedd}).

@@

@@

The study of special embeddings was traces back to fundamental papers by Eugene Dynkin
\cite{dynkin1952semisimple,dynkin1952maximal}, he called such subalgebras ``S-subalgebras'' to
distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
of the algebra root system. While maximal regular subalgebras have complete classification, the case
of special subalgebras is more difficult.

Denote Lie algebra by $\mathfrak{g}$, we assume that it is simple. Let's denote a subalgebra by
$\mathfrak{a}$. To construct an embedding of special subalgebra $\mathfrak{a}\to \mathfrak{g}$ one
needs to consider some representation of $\mathfrak{a}$ of dimension $\mathrm{dim}\mathfrak{g}$ and
identify generators of $\mathfrak{a}$ with linear combinations of generators of $\mathfrak{g}$ in
the adjoint representation.

 Such subalgebras are constructed by considering
representation of the algebra to

Projection of $\mathfrak{g}$ root system to the root space of $\mathfrak{a}$ in many cases can be
encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
Number of roots in projection is equal to the number of roots in $\mathfrak{g}$ root system (We do
not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
the rank of subalgebra $\mathfrak{a}$. Having Lie algebra $\mathfrak{a}$ and augmented Dynkin
diagram of the same rank it should be possible to reconstruct the embedding $\mathfrak{a}\to
\mathfrak{g}$, though not always in a unique way.

(We have the dimension of representation of $\mathfrak{a}$ and projection of roots of
$\mathfrak{g}$. It's not enough since in general there are different non-equivalent representations
of $\mathfrak{a}$. But the number of simple root systems with given number of roots is finite, so
it's possible to check which one has given projection).

Classification of all splints for special embeddings of a given algebra $\mathfrak{a}$ is given by
the augmented Dynkin diagrams of the same rank. (!)

@@

@@

В приложении к присоединенному представлению эта теорема означает, что в ортогональной проекции
корневой системы алгебры $g$ на корневое пространство подалгебры $a$ содержится корневая система
подалгебры $a$. Более того, верна следующая теорема:

@@

Relying on these theorems we can encode the projections of root system by Dynkin diagrams. We need
to allow simple roots to have non-trivial multiplicities.

Classification of special embeddings

\begin{theorem}\label{va1}
Вложения
\begin{itemize}
\item $so(n-1)\rightarrow so(n)$,
\item $so(n)\rightarrow su(n)$,
\item $su(n)\rightarrow sp(2n)$,
\item $su(n-1)\rightarrow su(n)$,
\item $sp(n)\rightarrow su(2n)$
\end{itemize} -- все максимальные специальные вложения класса $A$ простых алгебр в простые алгебры (некоторые вкладываемые алгебры просты с точностью до фактора $u(1)$);
вложения
\begin{itemize}
\item $so(n)\oplus so(m)\rightarrow so(n+m)$
\item $su(n)\oplus su(m)\rightarrow su(n+m)$
\item $sp(n)\oplus sp(m)\rightarrow sp(n+m)$
\item $so(n)\oplus so(m)\rightarrow so(nm)$
\item $su(n)\oplus su(m)\rightarrow su(nm)$
\item $so(n)\oplus sp(m)\rightarrow sp(nm)$
\item $sp(n)\oplus sp(m)\rightarrow so(4nm)$
\end{itemize} -- все максимальные специальные вложения класса $A$ полупростых алгебр в простые алгебры \cite {sp1}.
\end{theorem}

\begin{theorem}\label{va2}
Не существует максимальных вложений класса $B$ полупростых (но не простых) алгебр в простые классические алгебры Ли. Если же вложение класса $B$ в простую алгебру $g$ строится на представлении $d$ размерности $p$, то оно может быть максимальным, только если $d$ неприводимо и:
\begin{itemize}
\item $g=so(n)$, $d$ -  ортогональное представление, $n=p$,
\item $g=sp(n)$, $d$ -  симплектичное представление, $n=p/2$,
\item $g=su(n)$, $d$ -  не ортогональное и не симплектичное представление, $n=p$.
\cite {sp1}
\end{itemize}
\end{theorem}

Эта теорема позволяет в подавляющем большинстве случаев определять максимальность вложения, не строя его явно.\\

Максимальные вложения класса $B$ приведены в таблице \ref{max-embeddings-class-B} (ну или еще какая-то текстовая связка-объяснение таблицы).

\begin{table}[h]

\label{max-embeddings-class-B}
\caption{Максимальные вложения класса $B$ в алгебры $so(2n)$, $so(2n-1)$, $su(n)$, $sp(2n)$ для $n\le 20$ \cite {sp1}.}
\begin{tabular}[t]{|p{3em}|p{20em}|}
\hline
 $a$ & $g$\\
\hline
$ sp(2)$ & $so(10)$, $so(14)$, $sp(8)$, $sp(10)$, $sp(20)$, $so(20)$  \\
\hline
$ su(3)$ & $su(6)$, $so(8)$, $su(10)$, $su(15)$, $so(27)$  \\
\hline
$ su(4)$ & $so(15)$, $su(10)$, $su(20)$, $so(20)$  \\
\hline
$ sp(3)$ & $so(14)$, $sp(7)$, $su(21)$ \\
\hline
$ so(7)$ & $so(8)$, $so(21)$, $so(27)$ \\
\hline
$ su(5)$ & $su(10)$, $su(15)$, $so(24)$ \\
\hline
$ sp(4)$ & $so(27)$, $so(36)$ \\
\hline
$ so(8)$ & $so(28)$, $so(35)$ \\
\hline
$ so(9)$ & $so(36)$ \\
\hline
$ su(6)$ & $su(15)$, $sp(10)$, $so(35)$ \\
\hline
$ so(10)$ & $su(16)$ \\
\hline
$ so(12)$ & $sp(16)$ \\
\hline
$ G_2$ & $so(7)$, $so(14)$ \\
\hline
$ F_4$ & $so(26)$ \\
\hline
\end{tabular}

\end{table}

@@

>>>>

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfa}{\hf_{\af}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}

@@

\begin{abstract}
  Splint is a decomposition of root system into union of root systems. Splint of root system for
  simple Lie algebra appears naturally in studies of (regular) embeddings of reductive subalgebras.
  Splint can be used to construct branching rules. We consider special embedding of Lie subalgebra
  to Lie algebra. We classify projections of algebra root systems using extended Dynkin diagrams and
  single out the conditions of splint appearance and coincidence of branching coefficients with
  weight multiplicities. While such a coincidence is not very common it is connected with Gelfand-Tsetlin basis. 
\end{abstract}

@@

The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
is the decomposition of root system into disjoint union of images of two or more embeddings of some
other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a
bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector
composition law in $\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

@@

In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
coincidence of branching coefficients with weight multiplicities under certain conditions. We denote
Lie algebra by $\gf$ and consider it's subalgebra $\af$. If $\af$ is a regular subalgebra, its root
system $\Delta_{\af}$ is contained in $\Delta_{\gf}$. Branching coefficients $b^{(\mu)}_{\nu}$
appear in decomposition of irreducible representation $L^{\mu}_{\gf}$ of $\gf$ to the sum of
irreducible representations of $\af$:
\begin{equation}
  \label{eq:1}
  L^{\mu}_{\gf}=\bigoplus_{\nu} b^{(\mu)}_{\nu} L^{\nu}_{\af}
\end{equation}

Assume that root system $\Delta_{\gf}$ splinters as $\Delta_{\gf}=\Delta_{\af} \cup
\phi(\Delta_{\sfr})$, where $\phi$ is an embedding of root system $\Delta_{\sfr}$ of some semisimple
Lie algebra $\sfr$. Then branching coefficients $b^{(\mu)}_{\nu}$ for the reduction
$L^{(\mu)}_{\gf}\downarrow \af$ coincide with weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in
$\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
Highest weight $\tilde\mu$ of $\sfr$-representation is calculated from Dynkin labels of highest
weight $\mu$ of $\gf$-module.

In next section \ref{sec:splints-root-systems} we review the classification of splints for simple
root systems and results for branching coefficients. Then we move to the study of special embeddings
which is the main subject of the present paper. We consider special embeddings of Lie subalgebras
into Lie algebra. In this case root system of the subalgebra is not contained in the root system of
the algebra. So the original motivation for splints is not applicable. But we can consider the
projection of root system of algebra on the root space of the subalgebra. Such a projection is not a
root system anymore, but it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is
possible to classify most projections using Dynkin diagrams augmented with multiplicities. We then
define splint for such 'weak' root systems and state the conditions of its appearance and
implications for the calculation of branching coefficients (Section \ref{sec:splints-spec-embedd}).

Use of representation theory of the subalgebra allows us to classify all the splints for the projections
of algebra root system. We also apply this method to metric splints and regular subalgebras and get
a unified treatment. We obtain Gelfand-Tsetlin rules for regular and special embeddings this way.

@@

\section{Splints of root systems and regular subalgebras}
\label{sec:splints-root-systems}
The notion of splint was introduced in the paper \cite{richter2008splints} and classification of
splints for simple root systems was obtained there.

Embedding $\phi$ of a root system $\Delta_1$ into a root system
$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
subset of $\Delta$ that commutes with vector composition law in
$\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that the image $Im(\phi)$ must not inherit the root system
properties except the addition rules equivalent to the addition
rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
can splinter $\Delta$  when the latter can be presented 
as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.

The classification is shown in table

Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
is a
reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
$\mathfrak{a}$,
this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
to be a proper regular subalgebra and $\mathfrak{a}$ to be the
maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.

Computation of branching coefficients relies on roots $\Delta_{\gf}\setminus \Delta_{\af}$
\cite{2010arXiv1007.0318L} so splint  is naturally connected branching coefficients for regular
subalgebra.

Remember that only three types of splints are
injective and thus are naturally connected with branching. Below we
reproduce the part of the splints table from \cite{richter2008splints} corresponding to
injective splints:
\begin{equation}
\label{eq:1}
\begin{array}{cc||c|c}
\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
\\ \hline\hline
\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
& F_{4} & D_{4} & D_{4} \\ \hline
\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
(*)& C_{r}(r\geq 3) & \oplus ^{r}A_{1} &  D_{r} \\ \hline
\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
^{r}A_{1} \\
& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
\end{array}
\end{equation}

Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
first type splints are equivalent and in the second are not. In the third
type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
the principle properties of branching but makes it possible to use the
multiplicities of $\frak{s}$ -modules without further projecting their
weights.

Note that in the case of $C_{r}$-series (marked with the star in table \eqref{eq:1}) metrical
embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of regular subalgebra
$\mathfrak{a}$ (See \cite{dynkin1952semisimple}).

In the paper \cite{2011arXiv1102.1702L} it was shown that

\begin{Prop}
\begin{equation}
\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
\label{singular main-4}
\end{equation}
Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
\[
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
\]
\end{Prop}
%% Rewrite this property informally

@@

The study of special embeddings was traces back to fundamental papers by Eugene Dynkin
\cite{dynkin1952semisimple,dynkin1952maximal}, he called such subalgebras ``S-subalgebras'' to
distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
of the algebra root system. While regular subalgebras are easy to construct by dropping nodes from
extended Dynkin diagram of the algebra, the case of special subalgebras is more difficult. Complete
classification for exceptional Lie algebras was obtained recently in \cite{minchenko2006semisimple}.
The algorithm of construction of special subalgebras is available in GAP package but still requires
manual intervention \cite{de2011constructing}.

Assume that Lie algebra $\gf$ is simple. Let's denote a subalgebra by
$\af$. We denote corresponding Cartan subalgebras by $\hfg$ and $\hfa$ and identify them with the dual
spaces $\hfg^{*}$, $\hfa^{*}$ using Killing forms of $\gf$ and $\af$.

To construct an embedding $\af\to\gf$ consider some representation $L^{\nu}_{\af}$ as a subspace of
Lie algebra $\gf$. Then one needs to check that the generators of $\af$ then can be presented as
linear combinations of generators of $\gf$. We can identify Cartan subalgebra $\hfa\subset \af$ with
dual space $\hfa^{*}$ using Killing form. Then the root system $\Delta_{\gf}$ of $\gf$ can be
projected to $\hfa^{*}$ using the expression of $\hfa$-generators through $\hfg$-generators.

%%  To reduce $\gf$-representations project $\gf$ root system to Cartan subalgebra of $\af$. 
%% 
%%  To construct an embedding of special subalgebra $\af\to \gf$ one
%% needs to consider some representation of $\af$ of dimension $\mathrm{dim}\gf$ and
%% identify generators of $\af$ with linear combinations of generators of $\gf$ in
%% the adjoint representation. 
%% 
%%  Such subalgebras are constructed by considering
%% representation of the algebra to
%%

From classical papers \cite{dynkin1952semisimple,dynkin1952maximal} it is well known that the
projection of $\gf$ root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
finite-dimensional but not irreducible representation of $\af$. Moreover, roots of $\af$ are
contained in this projection. We denote such a projection by
\begin{equation}
  \label{eq:2}
  \Delta'=\pi_{\af}\left(\Delta_{\gf}\right)
\end{equation}

The system $\Delta'$ can be a root system but it can be not reduced and can contain some vectors
with multiplicities greater then one.

@@

To

@@

Applying this theorem
В приложении к присоединенному представлению эта теорема означает, что в ортогональной проекции
корневой системы алгебры $g$ на корневое пространство подалгебры $a$ содержится корневая система
подалгебры $a$. Более того, верна следующая теорема:

@@

%% Relying on these theorems we can encode the projections of root system by Dynkin diagrams. We need
%% to allow simple roots to have non-trivial multiplicities. 
%%

@@

Since roots are weights of the adjoint representation, such a projection produces the weight diagram
of $\af$-representation that contains adjoint representation of $\af$. After the subtraction of
$\af$-root system $\Delta_{\af}$ from $\Delta'$ we obtain weight diagram of representation called
``characteristic representation of subalgebra $\af$'' by Dynkin in the seminal paper
\cite{dynkin1952semisimple}.

We want to classify all the cases when branching coefficients coincide with weight multiplicities of
some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
$\gf$ root system admits a splint $\Delta=\Delta_{\af}\cup \Delta_{\sfr}$. Projection of the root
system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation of
algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
representation of $\af$ and can be decomposed as
\begin{equation}
  \label{eq:3}
  \mathrm{ad}_{\gf}=\mathrm{ad}_{\af}\oplus M_{\af}^{\chi},
\end{equation}
where $M^{\chi}_{\af}$ is not necessary irreducible representation of $\af$ called
``characteristic'' in \cite{dynkin1952semisimple}.

Weight diagram of $M^{\chi}_{\af}$ coincides with root system $\Delta_{\sfr}$ with the exception of
zero weight. So we need to find all the representations for all simple Lie algebras $\af$, such that
their weight diagrams are root systems after the exclusion of zero weight.

Multiplicity of zero weight in adjoint representation is equal to the rank of the algebra. So if
$\mathrm{rank}\gf-\mathrm{rank}\af$, the representations in questions must be multiplicity-free.

The simplest class of multiplicity-free representations is called ``strongly multiplicity free''
\cite{lehrer2006strongly} and consists of multiplicity free representations with weight systems
admitting strict ordering $\nu_{1}<\nu_{2} \Leftrightarrow \nu_{1}=\nu_{2}+n \alpha$, where $n\in
\mathbb{N}, \alpha\in \Delta^{+}_{\af}$ and for all $\nu_{1},\nu_{2}$ either $\nu_{1}<\nu_{2}$ or
$\nu_{2}<\nu_{1}$.

The list of strongly multiplicity free representations consists of (first) fundamental representations
for series $A_{r}, B_{r}, C_{r}$, exceptional Lie algebra $G_{2}$ (7-dimensional representation) and
all $A_{1}$ representations.

First fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
multiplicity-free branching for the embedding $so(2r+1)\to so(2r+2)$.

Fundamental weights of the algebra $A_{r}$ are shorter than its roots, but the projections of $\gf$
weights must be given by linear combinations of roots of special subalgebra $\af$ with integer
coefficients, so the first class of strongly multiplicity free representations does not produce such
projection.

Nevertheless, the union of diagrams of two fundamental representations of $A_{2}$ with the root
system of $A_{2}$ produces weight diagram of $G_{2}$. This case corresponds to splint
$\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$ which is connected
with regular subalgebra $A_{2}\subset G_{2}$ (see Section \ref{sec:splints-root-systems}).

The complete classification of multiplicity-free irreducible representations was obtained in
\cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}).

What we really need is the classification of all the representations where multiplicities of all
non-zero weights are equal to one. Fortunately, such a classification was obtained in
\cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
representations of algebras $B_{r}$.

 (Possibly, strongly multiplicity-free:
).

 Classification of strongly multiplicity-free representations is simple:
$A_{n}$ first fundamental representation, $B_{n}$ first fundamental representation, $C_{n}$ first
fundamental representation, $G_{2}$ first fundamental representation (7) and
all irreducible $A_{1}$-representations.

(See also https://projecteuclid.org/euclid.jmsj/1180135505 for multiplicity-free branching rules)

Having obtained this classification we need to check which weight diagrams can be obtained as the
projections of $\gf$ root system. It is the case for $B_{n}\to D_{n+1}$ or $A_{1}\oplus\dots\oplus
A_{1}\to D_{n+1}$.

Projection of $\gf$ root system to the root space of $\af$ in many cases can be
encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
Number of roots in projection is equal to the number of roots in $\gf$ root system (We do
not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
the rank of subalgebra $\af$. Having Lie algebra $\af$ and augmented Dynkin
diagram of the same rank it should be possible to reconstruct the embedding $\af\to
\gf$, though not always in a unique way.

We must also account for the case of roots of parallel roots of different length. $BC_{1} $ is the
simplest system with parallel roots, one of its two parallel is twice longer than another. Such a
system appear in study of affine

 The simplest
system with parallel roots have roots of two different length and Such a systems
appear  $BC_{1} $ and its generalization. (We have the dimension of representation of $\af$ and
projection of roots of $\gf$. It's not enough since in general there are different non-equivalent
representations of $\af$. But the number of simple root systems with given number of roots is
finite, so it's possible to check which one has given projection).

Classification of all splints for special embeddings of a given algebra $\af$ is given by
the augmented Dynkin diagrams of the same rank. (!)
